Modelling the emergence of whisker barrels

### 2020-05-23 paper/briefpaper/brief.tex
Back down to 3 main equations, because the sigmoid transfer function turns out to be unnecessary in comop2

The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
% EITHER
%%redefined
%%%
%%\begin{equation} \label{eq:comp}
%%\color{blue}
%%\chi_i(\mb{x}, t) = \frac{\bar{a}_i F}{N-1} \nabla \sum_{j\ne i}{a_j}
%%\color{black}
%%\end{equation}
% OR
\cmnt{first define a quantity to represent the branching density of all
  \emph{other} TC types; $\hat{a}_i = \sum_{j\ne i}{a_j}$; then set the term
  $\chi_i$ to be}
%
\begin{equation} \label{eq:comp}
\color{blue}
\chi_i(\mb{x}, t) = \frac{\bar{a}_i F}{N-1} \nabla \hat{a}_i
\color{black}
\end{equation}

%
\cmnt{where $F$ is a parameter and $\bar{a}_i$ is a bounded version of $a_i$
  obtained by passing the branching density through the sigmoid function}
%
\begin{equation} \label{eq:abar}
\color{blue}
  \bar{a}_i = \frac{2}{1+\mathrm{e}^{5 - 0.5 a_i}}.
\color{black}
\end{equation}
%
\cmnt{In this expression for $\bar{a}_i$ (only), we model the idea
 that there must be an upper bound on the axonal branching density.}

\cmnt{which contributes to the \emph{flux of axonal branching} by making branching
  density for each projection `flow away' from regions} where the branches of
other projections are dense. Note that this operation is local to individual
afferent projections.

@@

A cortical boundary enclosing 41 corresponding barrels was traced from a
cytochrome oxidase stain from \cite{zheng_signal_2001}, and
Eqs.~\ref{eq:dc}--\ref{eq:norm} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes. From random initial conditions for
$a(\mb{x},0)$ and $c(\mb{x},0)$, a clear Voronoi-like tesselation emerged
(Fig.\,1C; see Movie S1). A reduction in the Honda delta metric (see
\citealp{senft_mouse_1991}) confirmed that a `good' Voronoi pattern emerged
within $\approx 3000$ iterations (Fig.\,1D). A measure of the difference
in shape between real and simulated barrels revealed a strong correspondence
(see Fig.\,1D).

>>>>

The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
% EITHER
%%redefined
%%%
%%\begin{equation} \label{eq:comp}
%%\color{blue}
%%\chi_i(\mb{x}, t) = \frac{\bar{a}_i F}{N-1} \nabla \sum_{j\ne i}{a_j}
%%\color{black}
%%\end{equation}
% OR
\cmnt{first define a quantity to represent the branching density of all
  \emph{other} TC types; $\hat{a}_i = \sum_{j\ne i}{a_j}$; then set the term
  $\chi_i$ to be}
%
\begin{equation} \label{eq:comp}
\color{blue}
\chi_i(\mb{x}, t) = \frac{a_i F}{N-1} \nabla \hat{a}_i,
\color{black}
\end{equation}
%
\cmnt{which contributes to the \emph{flux of axonal branching} by making
  branching density for each projection `flow away' from regions} where the
branches of other projections are dense. \cmnt{$F$ parameterizes the strength
  of this competitive interaction.} Note that this operation is local to
individual afferent projections.

@@

A cortical boundary enclosing 41 corresponding barrels was traced from a
cytochrome oxidase stain from \cite{zheng_signal_2001}, and
Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes. From random initial conditions for
$a(\mb{x},0)$ and $c(\mb{x},0)$, a clear Voronoi-like tesselation emerged
(Fig.\,1C; see Movie S1). A reduction in the Honda delta metric (see
\citealp{senft_mouse_1991}) confirmed that a `good' Voronoi pattern emerged
within $\approx 3000$ iterations (Fig.\,1D). A measure of the difference
in shape between real and simulated barrels revealed a strong correspondence
(see Fig.\,1D).
